Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-07-17 manuscript.tex
Add files via upload
minor updates. Only one last comment in Sec.7 to be checked.

For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
planet, we used a non-linear least squares for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid being blocked in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).

>>>>

For each of the 4500 simulations we derived at first the corresponding three set of RV, namely N mean RV, SN mean RV and SN median RV. 
On each of those RV sets, we performed an analysis similar to Sec.~\ref{sec:soap.spot.planet}, i.e. fitting the activity signal using Eq.~\eqref{eq:RV:correction}
or the usual correction along with a circular planetary signal (see Eq.~\eqref{eq:RV:correction.overall}). Because of the non-linearity of the model to account for the
planet, we used a non-linear least squares for the fit \citep[][]{levenberg1944method,marquardt1963algorithm,teunissen1990nonlinear}. Such a model requires
initial conditions close to the real solution, otherwise the algorithm can converge to a local minimum. Because our goal here is to compare the planetary detection limits
using the three different RV estimates and the two different activity model proposed, and not to discuss what is the best method to explore the parameter space, we 
initialised the minimisation algorithm to the real period of the planetary signal injected to avoid to get stuck in a local minimum. We also selected as initial amplitude the peak-to-peak amplitude of the RV data set.
The argument of periapsis $t_0$ was initialised to the time when the RV were crossing 0 since we use a sinusoidal function to fit the planetary signal (see Eq.~\eqref{eq:RV:correction.planet}).
